Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-02-10 constantRate/ConstCompFuzzExt.tex
small edits to intro

\begin{abstract}
Fuzzy extractors convert a noisy source of entropy into a consistent uniformly distributed key.  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns. We call what is left after this worst-case loss the \emph{minimum usable entropy}.  Unfortunately, this quantity is negative for some sources that are important in practice. Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used for such sources.

@@

Our first construction requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.  Our second construction requires  a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.

\iffalse
For many practical noisy sources, like biometrics, the minimum usable entropy is negative, leaving reliable key derivation from these sources as an open problem.

Traditionally, their security is defined information-theoretically.  %Fuzzy extractors have upper bounds on the length of the derived key.

Fuzzy extractors work for any distribution with enough entropy.  %In this setting, the entropy of the source must be significantly higher than the logarithm of number of error patterns corrected~(Dodis et al., J. of Comp 2008).

We call the difference between the starting entropy and the logarithm of the number of correctable error patterns the \emph{minimum usable entropy}.  Dodis et al.~(J. of Comp. 2008) show there is some source where the key length cannot exceed the minimum usable entropy.  Therefore, fuzzy extractors that output the same length key for any source with enough entropy cannot output a key longer than the minimum usable entropy.

%Traditional fuzzy extractors output a key roughly of length minimum usable entropy.
To achieve meaningful security when the minimum usable entropy is negative, some restriction on the source is necessary.  Meaningful restrictions (and accompanying constructions) have proved elusive for information-theoretic fuzzy extractors.
Fuller, Meng, and Reyzin (Asiacrypt 2013) define a computationally-secure version of a fuzzy extractor.  It may be easier to construct computational fuzzy extractors for meaningful sources.

In this work, we construct the first (computational) fuzzy extractors that are secure for a large class of distributions where the minimum usable entropy is negative.

\textbf{Constructions:}  We construct computational fuzzy extractors from point function obfuscation.
Our constructions are inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~(Eurocrypt 2008).
\bnote{this whole paragraph needs work} Our two constructions are similar in spirit but optimize different parameters.  The first requires individual blocks of the source to have super-logarithmic entropy and corrects a constant fraction of errors.  The second construction uses sampling to reduce the required entropy of the source.  Unfortunately, sampling also reduces the effective error tolerance of the construction.  %The first construction works for high-entropy and high-error sources, while the second construction works for distributions with lower entropy and error.
\bnote{need something else to say here}
\fi
\end{abstract}

@@

Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}. We define and show two constructions of \emph{computational fuzzy conductors}.
These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).

@@

Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates). We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into to a string of blocks and then applies the first construction. $\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block. This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance. This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.  Unlike in locally computable extractors, we can form multiple blocks sampling from the same value $w$ and only argue about their individual entropy, because correlations among blocks are allowed for the first construction. Computational, rather than information-theoretic, analysis seems crucial for achieving this property.

\paragraph{On the Relationship to General Obfuscation}
We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within distance $t$ of $w$. However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions. Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs. However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model. The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero. However, we do not know if these functions include proximity point programs.

@@

Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within distance $t$ of $w$. The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$. Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree). Constructing an efficient obfuscator for proximity queries when $\Huse<0$ is an open problem.

>>>>

\begin{abstract}
Fuzzy extractors convert a noisy source of entropy into a consistent uniformly distributed key.  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns. We call what is left after this worst-case loss the \emph{minimum usable entropy}.  Unfortunately, this quantity is negative for some sources that are important in practice. Most known approaches for building fuzzy extractors work in the worst case and cannot be used when the minimum usable entropy is negative.

@@

Our first construction requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.  Our second construction requires  a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. The constructions can be implemented efficiently based on number-theoretic assumptions or assumptions on cryptographic hash functions.
\end{abstract}

@@

Any procedure that converts a high-entropy input to a high-entropy output is known as a \emph{conductor} \cite{CRVW02}; if it's error-tolerant, then it's a \emph{fuzzy conductor}~\cite{KanukurthiR09}. We show two constructions of \emph{computational fuzzy conductors}.
These constructions may be converted to computational fuzzy extractors using information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractors~(\lemref{lem:cond and cext}).

@@

Obfuscation of point functions provides no security if a point can be guessed; thus, in order for the first construction to be secure, sufficiently many coordinates of $w$ have to be unguessable (even to an adversary who can make equality queries for the values of other coordinates). We relax this requirement in our second construction (\consref{cons:sampling}), called \emph{sample-then-obfuscate}: it transforms $w$ into a string of blocks and then applies the first construction. $\gen$ randomly samples several coordinates of $w$ and concatenates them to form a block. This reduces the entropy requirement on the individual symbols, but lowers the error-tolerance. This approach is similar to the sample-then-extract paradigm for building locally computable extractors~\cite{lu2002hyper,vadhan2003constructing}.  Unlike in locally computable extractors, we can form multiple blocks sampling from the same value $w$ and only argue about their individual entropy, because correlations among blocks are allowed for the first construction. Computational, rather than information-theoretic, analysis seems crucial for achieving this property.

\paragraph{On the Relationship to General Obfuscation}
We note that fuzzy extractors for the setting where $\Huse\le 0$ can be trivially constructed from a strong form of obfuscation, specifically, virtual black-box obfuscation for the class {\em proximity point programs}, $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. However, currently we do not know if such obfuscation exists, let alone whether it can be made as efficient as our constructions. Recent works constructed candidate indistinguishability obfuscators \cite{GargGH0SW13,PassTS13} and virtual black-box obfuscators in an idealized model \cite{BrakerskiR13,BarakGKPS13} for all programs. However, these notions of obfuscation do not imply virtual-black-box obfuscation for proximity point programs in the plain model. The work of \cite{BarakBCKPS13} suggests an average-case virtual-black-box obfuscator for the family of {\em evasive} functions that test if a low-degree multi-variant arithmetic circuit evaluates to zero. However, we do not know if these functions include proximity point programs.

@@

Using information-theoretic fuzzy extractors with additional privacy properties, Dodis and Smith~\cite[Section 5]{DBLP:conf/stoc/DodisS05} construct program obfuscators for the program $I_w(x)$ that tests if $x$ is within Hamming distance $t$ of $w$. The obfuscation is secure as long as $w$ comes from a distribution of sufficient min-entropy; in particular, the entropy must be high enough so that $\Huse>0$. Our constructions do not provide obfuscators for proximity queries, because they leak more information than whether $x$ is within distance $t$ of $w$ (for example, they may provide some information about the actual distance or about which coordinates agree). Constructing an efficient obfuscator for proximity queries when $\Huse<0$ is an open problem.
